Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-20 paper/paper.tex
Updating the model

Short ocean surface waves are modulated by longer swell.
Following \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced a steady, approximate solution for
hydrodynamic modulation of short waves by longer waves:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result influenced the development of remote sensing of ocean
surface waves and currents \citep{keller1975microwave,hara1994hydrodynamic}.
\citet{phillips1981dispersion} and \citet{longuet1987propagation} revisited this
problem by nonlinear long waves and variations in the effective gravity of short
waves, yielding significantly stronger modulation than previously predicted.
\citet{henyey1988energy} derived an analytical solution for the modulation of
short waves by long waves using Hamiltonian mechanics and reported the modulation
of similar magnitude to that of \citet{longuet1987propagation}.
\citet{zhang1990evolution} considered weakly nonlinear short waves
using a non-linear Schr\" odinger equation and found stronger wavenumber
modulation but weaker amplitude modulation than those predicted by
\citet{longuet1987propagation}.
The variety of analytical and numerical frameworks (Eulerian, Hamiltonian,
Schr\" odinger) that relatively closely reproduce steady solutions for short-wave
modulation suggests that the solutions are robust.
Alternative analytical and numerical approaches to the modulation problem remain
of interest, especially if higher degrees of nonlinearity can be considered
using simpler approaches.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/fig_modulation_ramp_timeseries.png}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \label{fig:unsteady_growth_timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/inhomogeneity_tendencies.png}
  \caption{
    Propagation ($C_g \frac{\partial N}{\partial x}$) (blue) and inhomogeneity
    ($N \frac{\partial C_g}{\partial x}$) (orange) tendencies and their sum
    (green) for the short-wave action after one long-wave period, in the case of
    (a) infinite long-wave train and (b) linear ramp of long-wave amplitude.
    Dashed line is the long-wave elevation and the dotted line is the short-wave
    action modulation minus 1.
  }
  \label{fig:inhomogeneity_tendencies}
\end{figure}

@@

\section{Sensitivity to wavenumber ratios}
\label{section:sensitivity_to_wavenumber_ratios}

\section{Scale analysis}
\label{section:scale_analysis}

Now that we showed that the analytical solution is consistent with full numerical
solutions for $\varepsilon_L < 0.25$, we can use analytical solutions for scale
analysis to quantify the relative contribution of tendencies in the full equation set.

TODO

>>>>

Short ocean surface waves are hydrodynamically modulated by longer swell.
Following \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced a steady, approximate solution for
hydrodynamic modulation of short waves by longer waves:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This hydrodynamic modulation process was instrumental for the development and
interpretation of remote sensing of ocean surface waves and currents
\citep{keller1975microwave,hara1994hydrodynamic}, and is distinguished
from the aerodynamic modulation process \citep{donelan1987effect,belcher1999wave,chen2000effects}.
\citet{phillips1981dispersion} and \citet{longuet1987propagation} revisited the
hydrodynamic modulation problem by considering nonlinear long waves and
variations in the effective gravity of short waves.
Their results yielded significantly stronger modulation than previously predicted.
\citet{henyey1988energy} derived an analytical solution for the modulation of
short waves by long waves using Hamiltonian mechanics and reported the modulation
of similar magnitude to that of \citet{longuet1987propagation}.
\citet{zhang1990evolution} considered weakly nonlinear short waves
using a non-linear Schr\" odinger equation and found stronger wavenumber
modulation but weaker amplitude modulation than those predicted by
\citet{longuet1987propagation}.
The variety of analytical and numerical frameworks (Eulerian, Hamiltonian,
Schr\" odinger) that relatively closely reproduce steady solutions for short-wave
modulation suggests that the solutions are robust.
Alternative analytical and numerical approaches to the modulation problem remain
of interest, especially if higher degrees of nonlinearity can be considered
using simpler approaches.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/fig_modulation_ramp_timeseries.png}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \label{fig:unsteady_growth_timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/inhomogeneity_tendencies.png}
  \caption{
    Propagation ($C_g \frac{\partial N}{\partial x}$) (blue) and inhomogeneity
    ($N \frac{\partial C_g}{\partial x}$) (orange) tendencies and their sum
    (green) for the short-wave action after one long-wave period, in the case of
    (a) infinite long-wave train and (b) linear ramp of long-wave amplitude.
    Dashed line is the long-wave elevation and the dotted line is the short-wave
    action modulation minus 1.
  }
  \label{fig:inhomogeneity_tendencies}
\end{figure}

@@

\section{Discussion}
\label{section:discussion}
